First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-06-27 eg6-letters/incoherent/incoherent_prl.tex
more cleaning

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
 deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
 final state. The data were accumulated using a 6 GeV longitudinally polarized 
 electron beam incident on a pressurized $^4$He gaseous target placed in front 
 of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
 Accelerator Facility. The azimuthal angular ($\phi$) dependence of the BSA is 
 studied in a wide range of virtual photon and scattered proton 
 kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound nucleon has 
 been compared with the one on the free proton. In the whole kinematical region of our 
 measurements, the BSA on the bound nucleon is smaller by about $20\%$ to $30\%$, 
 indicating possible medium modification on the nucleon's partonic structure.  
 This measurement opens a new opportunity to explore the origin of the EMC 
 effect within the framework of the generalized parton distributions.

@@

In this Letter, we present the first exclusive measurement of the beam-spin asymmetry 
in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. 
Experimentally, we measure the squared sum of the Bethe-Heitler (BH) and the DVCS 
amplitudes, with the BH process the process where the real photon is emitted by 
the incident or the scattered electron rather than the nucleon. The beam-spin 
asymmetry arises from the interference of these two terms and is directly 
sensitive to the DVCS amplitude that contain the information on the GPDs. 
Using a longitudinally polarized electron beam (L) and an unpolarized target 
(U), this beam-spin asymmetry observable is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
Spectrometer (CLAS) coordinate center. For DVCS experiments, the CLAS baseline 
design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
The 5-Tesla solenoid magnet in the center of which the target was located 
prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS 
drift chambers by guiding these electrons inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected if an electron, a proton, and at least one 
photon were detected in the final state. Electrons were identified as negatively 
charged tracks reconstructed in drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a proper light yield in 
the Cherenkov counters. The protons were identified from positively charged tracks by 
timing analysis using the time-of-flight measured by the scintillator counters. 
In addition, it was required that both the electron and the proton in the event 
originated from the same vertex at the target within CLAS tracking vertex 
resolution. The photons were detected in either the IC or 
the CLAS electromagnetic calorimeter. All the clusters within the IC fiducial region 
were assumed to be photons, while a timing cut is used to clean the EC photons 
from neutrons. Note that even though the DVCS reaction has only one real photon 
in the final state, events with more than one photon were not discarded at 
this stage. These are mostly soft photons from accidental coincidence which, 
as will be discussed below, the DVCS exclusivity cuts eliminate easily. In the 
following selection stage, the most energetic photon is considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the 
particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, events were 
selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the applicability of the 
DVCS handbag diagram, and with $\gamma^{*}p$ invariant mass (W$=(q+p)^2$) greater than 2 GeV to 
avoid the nucleon resonance region. The transferred momentum squared to the recoil proton was required to be greater than a
minimum allowed value at given Q$^2$ and W ($t~>~t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
ensured by imposing constraints on the kinematical variables resulting from 
conserving the four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass 
squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables and applied cuts are shown in 
FIG.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
also rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 30k events passed all these requirements; their kinematic 
distributions are shown in FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The incoherent DVCS exclusivity cuts. The black distributions 
   represent the incoherent DVCS events candidate before all the exclusive 
   cuts. The shaded distributions represent the incoherent DVCS events which 
   passed all the exclusivity cuts except the quantity plotted. The vertical 
   red lines represent the applied exclusivity cuts. The distributions from 
   left to right and from top to bottoms are: $\Delta \phi$, missing energy,
   missing masses squared and the cone angle ($\theta$) between the measured 
   and the calculated photons in the $e'p'$ final-state system. }
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution 
was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using the data and 
simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
cuts to the number of identified $\pi^0$ events, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
kinematics, we found this contamination to be of 8\% to 10\%.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries than the calculations.  
These differences may arise from nuclear effects which are not taken into 
account in the model, such as long-range interactions. On the graph for $-t$ 
dependence, we show previous measurements by the HERMES collaboration
\cite{Airapetian:2009cga} using inclusive final state, ($e^\prime\gamma$). Due 
to large experimental uncertainties of HERMES points, the two measurements 
do not disagree, but we can also see that their high $-t$ results were 
smaller than expected by models.

>>>>

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He using the exclusive 
   final state. The data were accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   nucleon have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound nucleon is 
   smaller by about $20\%$ to $30\%$, indicating possible medium modification 
   on the nucleon's partonic structure.  This measurement opens a new 
   opportunity to explore the origin of the EMC effect within the framework of 
   the generalized parton distributions.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes, with the former is the process 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon. The beam-spin asymmetry arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs.  Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), this beam-spin asymmetry observable is 
defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS to very 
small polar angles, 4$^{\circ}$.  The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks by timing analysis using the time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target within CLAS tracking vertex resolution. The photons were detected in 
either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
the IC fiducial region were assumed to be photons, while a timing cut is used 
to clean the EC photons from neutrons. Note that even though the DVCS reaction 
has only one real photon in the final state, events with more than one photon 
were not discarded at this stage. These are mostly soft photons from accidental 
coincidence which, as will be discussed below, the DVCS exclusivity cuts 
eliminate easily. In the following selection stage, the most energetic photon 
is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton by assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
\cite{Hattawy:thesis} for additional details). We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. About 30k events 
passed all these requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The incoherent DVCS exclusivity cuts. The black distributions 
   represent the incoherent DVCS events candidate before all the exclusive 
   cuts. The shaded distributions represent the incoherent DVCS events which 
   passed all the exclusivity cuts except the quantity plotted. The vertical 
   red-dashed lines represent the applied exclusivity cuts. The distributions 
   from left to right and from top to bottoms are: $\Delta \phi$, missing 
   energy, missing masses squared and the cone angle ($\theta$) between the 
   measured and the calculated photons in the $e'p'$ final-state system. }
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution 
was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using the data and 
simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
cuts to the number of identified $\pi^0$ events, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of yield of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
kinematics, we found this contamination to be of 8\% to 10\%.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations.  These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions.  On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga} using inclusive final 
state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES 
points, the two measurements do not disagree, but we can also see that their 
high $-t$ results were smaller than expected by models.
